Ants-Review: A Protocol For Open Anonymous Peer-Reviews

### 2020-09-20 paper-v1.tex
Discussion: changes on 'A new standard'

\begin{figure}
\centering
\includegraphics[scale=0.28]{Ants-Review}
\small{
\caption{Exagones represent the protocol's smart contracts. Ellipse represents the smart contract inherited by AntsReview. Clouds represent integrations into the protocol. Rectangles represent smart contracts' libraries.
\textbf{a} Core contract of the protocol implementing a bounty system with the functions listed.
\textbf{b} Module inherited by AntsReview: it manages the access control of the protocol by adding and removing issuers and peer-reviewers.
\textbf{c} Native token used in the protocol. It is linked to (\textbf{a}), (\textbf{e}) and to (\textbf{d}).
\textbf{d} Faucet to distribute \emph{ANTS} on Kovan Testnet for testing purposes. 
\textbf{e} Integration with Aztec Protocol to wrap (\textbf{c}) into \emph{zkANTS} to implement private \emph{ANTS} transactions on Ethereum.
\textbf{f} Integration with IPFS to upload papers, requirements and peer-reviews and store the hash as \emph{PoE} into AntsReview.
\textbf{g} Integration with De-Fi services like \emph{Dai} and \emph{Chai}, to be used as tokens in the protocol.
\textbf{h} Library used by the protocol for secure contract development with the modules listed.}}
\label{fig:contracts}
\end{figure}

@@

\subsection{A new community-driven standard?}
As Tennant points out\cite{Tennant2017-F1000R}, a change is already happening in the publishing industry, especially with new born publishers opening up the review process (\emph{BioMed Central}, \emph{ELife}, \emph{Frontiers}, \emph{PeerJ}, \emph{F1000 Research}). If also pre-print platforms integrate peer-review into their platforms, the dissociation of initial scientific dissemination and scientific validation will force the publishing industry to adapt in order to keep up with the higher quality scientific process offered by alternative peer-review platforms and justify their added value (\emph{ibidem}).
In our proposal we decoupled the peer-review process from the publishers giving it back to the scientific community and applying concepts from mechanism design. We foresee that the future will evolve towards community-organized peer reviews: peer reviews will be more and more independent from publishers, and researchers will be the ones seeking the papers to review to build reputation within the community and not journals.
\newline Enlarging the pool of reviewers and accelerating the whole process might make Peer reviews requires a standard: building smart-contracts for peer-reviews might set a first step in this direction and our work seems promising. We hope that soon the value of peer review as 'academic capital' will be recognized by research funders and hiring committees.

>>>>

\begin{figure}
\centering
\includegraphics[scale=0.28]{AntsReview}
\small{
\caption{Exagones represent the protocol's smart contracts. Ellipse represents the smart contract inherited by AntsReview. Clouds represent integrations into the protocol. Rectangles represent smart contracts' libraries.
\textbf{a} Core contract of the protocol implementing a bounty system with the functions listed.
\textbf{b} Module inherited by AntsReview: it manages the access control of the protocol by adding and removing issuers and peer-reviewers.
\textbf{c} Native token used in the protocol. It is linked to (\textbf{a}), (\textbf{e}) and to (\textbf{d}).
\textbf{d} Faucet to distribute \emph{ANTS} on Kovan Testnet for testing purposes. 
\textbf{e} Integration with Aztec Protocol to wrap (\textbf{c}) into \emph{zkANTS} to implement private \emph{ANTS} transactions on Ethereum.
\textbf{f} Integration with IPFS to upload papers, requirements and peer-reviews and store the hash as \emph{PoE} into AntsReview.
\textbf{g} Integration with De-Fi services like \emph{Dai} and \emph{Chai}, to be used as tokens in the protocol.
\textbf{h} Library used by the protocol for secure contract development with the modules listed.}}
\label{fig:contracts}
\end{figure}

@@

\subsection{A new community-driven standard?}
As Tennant points out\cite{Tennant2017-F1000R}, a change is already happening in the publishing industry, especially with new born publishers opening up the review process (\emph{BioMed Central}, \emph{ELife}, \emph{Frontiers}, \emph{PeerJ}, \emph{F1000 Research}). If also pre-print platforms integrate peer-review into their platforms, the dissociation of initial scientific dissemination and scientific validation will force the publishing industry to adapt in order to keep up with the higher quality scientific process offered by alternative peer-review platforms and justify their added value (\emph{ibidem}).
In our proposal we decoupled the peer-review process from the publishers giving it back to the scientific community and applying concepts from mechanism design. We foresee that the future will evolve towards community-organized peer reviews: peer reviews will be more and more independent from publishers, and researchers will be the ones seeking the papers to review to build reputation within the community and not journals.
\newline Enlarging the pool of reviewers to potentially an entire scientific community and accelerating the whole process might require a new standard for peer reviews: for example some aspects might be taken over by AI assistants leaving to the reviewers the sole task of evaluating the content of a paper (such as \emph{AIRA} \cite{}). Building smart-contracts for peer-reviews might set a first step in this direction and our work seems promising. We hope that soon the value of peer review as 'academic capital' will be recognized by research funders and hiring committees.
